---
title: "General Dynamics Political Donations"
author: "Stephen Neukam"
date: "`r Sys.Date()`"
title-block-banner: true
format:
  html:
    #theme: cosmo
    layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute:
  echo: false
  warning: false
  message: false
---
```{css}

```

```{r}
###
# Load libraries
###
library(tidyverse)
library(janitor)
library(data.table)
library(rmarkdown)
library(devtools)
library(pacman)
devtools::install_github("kent37/summarywidget")
pacman::p_load(tidyverse, crosstalk, DT, lubridate, plotly, reactable, gt, summarywidget, here, glue, janitor, googlesheets4, googledrive, ggthemes, devtools, knitr, kableExtra,tidytext,textstem)
output_formatted_table = function(table, text, label_text = NULL){
  table %>%
    kable(caption = text, label = label_text) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 14, fixed_thead = T) %>%
    scroll_box(width = "100%")
}

###
# Loading in data
###
general_dynamics_donos <- read_csv("data/general_dynamics_donos.csv")

general_dynamics_donos <- general_dynamics_donos %>%
  select(committee_name, entity_type, recipient_name:recipient_zip, beneficiary_committee_name, disbursement_date:disbursement_amount, candidate_office, candidate_name)

###
# Top candidate donos from GD
###
top_ccm_recipients <- general_dynamics_donos %>%
  filter(entity_type == "CCM") %>%
  group_by(candidate_name, candidate_office) %>%
  summarise(total = sum(disbursement_amount)) %>%
  arrange(desc(total))

###
# Searchable, filterable and sortable table
###
# Remove columnDefs if you don't want to hide any columns
candidate_donos_table <- top_ccm_recipients |>
  datatable(
    filter = "top",
    extensions = c(
      "Buttons"
    ),
    rownames=FALSE,
    escape=FALSE,
    #    style="bootstrap",
    class="compact cell-border stripe",
    width="100%"
      )

total_candidate_contribs <- general_dynamics_donos %>%
  filter(entity_type == "CCM") %>%
  summarise(total = sum(disbursement_amount))

total_candidate_contribs <- paste(total_candidate_contribs)
```
## General Dynamics, the American company that makes the Abrams tanks that are being sent to Ukraine, has donated handsomely to the campaigns of congressional candidates. 
Since 2016, the company has donated to `r nrow(top_ccm_recipients)` candidates running for Congress. The donations amounted to over $`r total_candidate_contribs`. Here is a searchable table of those candidates and contributions.

### Table of General Dynamics candidate contributions since 2016
```{r}
candidate_donos_table
```


